PhD Research Proposal: Molecular Level Design of Nanoporous Lyotropic Liquid Crystal Membranes for Aqueous Separations \\ \vspace{0.5cm} \large Advisors: Michael Shirts and Richard Noble

### 2019-04-11 Ben_Manuscripts/comps/Outline.tex
Fixed up abstracts, filled in Objective 1 and 2 progress

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage[x11names,table]{xcolor}
\renewcommand{\baselinestretch}{1.5}
\usepackage{url}
\newcommand{\foo}{\color{LightSteelBlue3}\makebox[0pt]{\textbullet}\hskip-0.5pt\vrule width 1pt\hspace{\labelsep}}
\DeclareCaptionFont{blue}{\color{LightSteelBlue3}}
\usepackage{array,booktabs}

@@

@@

  \textbf{\large Objective 1:} \textit{\large Build and understand nanoscopic structure of LLC membranes} (\textcolor{green!40!olive}{\textbf{Complete}})

  \noindent We have developed a procedure for building an LLC membrane unit cell.

  \noindent We have created a molecular model that is maximally consistent with
  experimental WAXS data.

  \noindent Water is necessary to fully reproduce all features in the WAXS pattern.

  \noindent An ensemble of simulation trajectories best capture the system's 
  time averaged behavior.

@@

  \noindent We added additional water to our model to create the H\textsubscript{II} phase

  \noindent Water partitions into the distal tail region

  \noindent The pore structure changes

  \noindent We place 20 small polar solutes

  \noindent The mean squared displacements are not a monotonic function of solute MSD

  \noindent Solute behavior is subdiffusive.

  \noindent Subdiffusive behavior is a consequence of a hopping and trapping mechanism.

  \noindent There are three mechanisms of entrapment.

@@

  \noindent The distribution of hop lengths is approximately gaussian

@@

  \noindent We have developed a procedure to build the Q\textsubscript{I} phase.

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage[x11names,table]{xcolor}
\usepackage{setspace}
\usepackage[font=small]{caption}
\setstretch{1.5} % line spacing
\captionsetup[table]{font={stretch=1,small}} % line spacing in tables
\captionsetup[figure]{font={stretch=1,small}} % line spacing in figures
\usepackage{url}
% For timeline
\newcommand{\foo}{\color{LightSteelBlue3}\makebox[0pt]{\textbullet}\hskip-0.5pt\vrule width 1pt\hspace{\labelsep}}
\DeclareCaptionFont{blue}{\color{LightSteelBlue3}}
\usepackage{array,booktabs}

@@

  \graphicspath{{./figures/}}

@@

  \textbf{\large Objective 1:} {\large Build and understand the nanoscopic structure of LLC membranes} (\textcolor{green!40!olive}{\textbf{Complete}})

  \noindent Our first task was to develop a procedure for building and equilibrating 
  an atomistic LLC membrane system (see Figure~\ref{fig:assembly}).
  \begin{itemize}
    \item We built a monoclinic unit cell consisting of four pores.
    \item Each pore is composed of monomer columns, where each column
    consists of 20 monomers stacked on top of each other so that the 
    phenyl groups are coplanar with each other and the $xy$ plane. 
    \item The columns are oriented so that the hydrophilic monomer head
    groups face towards the pore center.
    \item We equilibrate the unit cell using a series of simulations
    with head groups held in place by position restraints. 
    \item We gradually reduce the force constant of the position 
    restraints until the system is completely unrestrained.
    \item We carried out 400 ns equilibration simulations.
  \end{itemize}

  \begin{figure}[!htb]
      \centering
      \begin{subfigure}{.3\textwidth}
              \centering
              \includegraphics[width=\textwidth]{NaGA3C11.pdf}
              \caption{}~\label{fig:monomer}
      \end{subfigure}
      \begin{subfigure}{.3\textwidth}
              \centering
              \includegraphics[width=\textwidth]{monomer_twocolor.pdf}
              \caption{}~\label{fig:atomistic_monomer}
      \end{subfigure}
      \begin{subfigure}{0.3\linewidth}
              \centering
              \includegraphics[width=0.6\textwidth]{wedge_thick.pdf}
              \caption{}~\label{fig:wedge}
      \end{subfigure}
              \begin{subfigure}{0.4\linewidth}
              \centering
              \includegraphics[width=0.6\textwidth]{columns.pdf}
              \caption{}~\label{fig:wedge_layer}
      \end{subfigure}
      \begin{subfigure}{0.4\linewidth}
              \centering
              \includegraphics[width=0.6\textwidth]{hexagonal_packing.pdf}
              \caption{}~\label{fig:hex_packing_simple}
      \end{subfigure}
      \caption{(a) The LLC monomer Na-GA3C11 (b) rendered atomistically (c)
      exhibits wedge-like character. (d) Monomers stack on top of each other to
      create columns with short range order, then assemble into pores with
      hydrophilic head groups (blue) facing towards the pore center. (e) The
      pores assemble into hexagonally packed columnar mesophases.}~\label{fig:assembly}
  \end{figure}

  \noindent We tested a number of different initial column architectures. 
  \begin{itemize}
      \item We stacked monomers in parallel displaced and sandwiched 
      configurations, two possible $\pi$-$\pi$ stacking modes.
      \item We also varied the initial distance between stacked monomers, $d$.
      \item We chose values of 3.7 \AA, based on experimental WAXS 
      measurements, as well as 5 \AA as a test of its sensitivity.
  \end{itemize}

  \noindent Our model's geometry is most consistent with experiment for systems
  built with 5 columns per pore and monomers initially stacked 3.7 \AA apart
  (see Figure~\ref{fig:p2p}). 
  \begin{itemize}
    \item We equilibrated systems with 4, 5, 6, 7 and 8 columns per pore.
    \item The pore spacing of 5 column-per-pore systems agree well with experiment.
    \item 6 column-per-pore systems built with $d$ = 5 \AA appear to yield an
    experimentally consistent pore spacing however, the equilibrated distance
    between stacked monomers stay close to 5 \AA which is inconsistent with 
    experiment. 
    \item In general, the equilibrated distance between monomers stays close to
    its initial value. 
  \end{itemize}

  \begin{figure}[!htb]
    \centering
    \includegraphics[width=\linewidth]{p2p.pdf}
    \caption{Systems with 5 columns per pore have equilibrated pore spacings
            closest to the experimental value of 4.12 nm. The equilibrated 
            pore spacing of the model increases as the number of columns in
            each pore increases.}~\label{fig:p2p}
  \end{figure}

%  \noindent On timescales that we can reasonably simulate, our equilibrated
%  structures show some initial configuration dependence. 
%  \begin{itemize}
%    \item All of the systems used to generate Figure~\ref{fig:p2p} are at 
%    least metastable.
%    \item We observe no large scale rearrangements that would be necessary
%    for all structures to converge to the same equilibrium structure. 
%  \end{itemize}

  \noindent We further validated the structure of our molecular model by 
  verifying its consistency with five major reflections present in the 
  experimental WAXS pattern.
  \begin{itemize}
    \item The five major reflections and the structural features leading
    to them are summarized in Figure~\ref{fig:WAXS_comparison}.
    \item Using MD trajectories, we simulated X-ray diffraction (XRD) 
    patterns that we could compare to the WAXS data by taking the 
    appropriate cross-section of the time-averaged 3D structure factor. 
    \item None of the models simulated to this point could reproduce R-double.   
  \end{itemize}

  \noindent It is necessary to add a small amount of water to our model in
  order to fully reproduce all features of the WAXS pattern.
  \begin{itemize}
    \item We built our most experimentally consistent structure in the 
    parallel displaced configuration with 1 wt \% water added to the 
    pores. 
    \item This is the only configuration that gives rise to the 
    R-double feature. 
    \item R-double appears because vertically adjacent monomer head groups
    hydrogen bond with shared water molecules, causing them to be drawn 
    closer together.
    \item When multiple pairing interactions occur in series along the 
    same pore axis, the center of masses of the pairs are spaced apart at 
    twice the $\pi$-stacking distance. 
  \end{itemize}

  %\begin{wrapfigure}{L}{0.5\textwidth}
  \begin{figure}[!htb]
  	\centering
    \begin{subfigure}{0.49\linewidth}
    	\includegraphics[width=\linewidth]{WAXS_annotated_words.pdf}
        \caption{Experiment}\label{fig:WAXS}
    \end{subfigure}
	\begin{subfigure}{0.49\linewidth}
        \includegraphics[width=\linewidth]{solvated_offset_rzplot_1.pdf}
        \caption{Simulation}\label{fig:solvated_XRD}   
	\end{subfigure}
    \caption{(a) 2D-WAXS gives details about repeating features on the order of
    angstroms. Our explanations for each of the 5 major reflections present are
    as follows: (R-$\pi$) Aromatic head groups $\pi-\pi$ stack 3.7 \AA~apart. 
    (R-double) Monomer head groups associate into pairs by hydrogen bonding with
    a shared water molecule. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. 
    (R-spots) Monomer tails pack hexagonally. (R-pores) The pores are spaced 
    4.12 nm apart and pack hexagonally. (b) We obtain a maximally consistent
    match between simulated XRD patterns and experimental WAXS data when we
    build systems in the parallel displaced configuration with 1 wt \% water
    included in the pores.}\label{fig:WAXS_comparison}
 \end{figure}
 %\end{wrapfigure}

  %BJC: I think this is important to say somewhere
  \noindent On the timescales that we can reasonably simulate, our model
  exhibits slow dynamics. 
  \begin{itemize}
    \item Consequently, there are very few uncorrelated frames in our 
    trajectories which leads to noise in the simulated XRD patterns. 
    \item We can overcome this issue by combining the structure factors
    generated from an ensemble of trajectories produced starting from 
    an ensemble of uncorrelated initial configurations.
  \end{itemize}

  \noindent The composition of the pores does not change regardless of which
  initial configuration we study.
  \begin{itemize}
    \item In Figure~\ref{fig:overlaid_densities}, we plot the radial density
    of various monomer components as a function of distance from the pore
    centers. 
    \item All are qualitatively similar meaning that a solute placed in 
    any of these systems should experience a similar chemical environment.
    \item Although we will move forward with our most promising configuration,
    this is an important finding since it implies that we do not need to apply
    the same level of rigor when screening new monomers.
  \end{itemize}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{regional_density_legend.pdf}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{head_group_density.pdf}
        \caption{Head Groups}
        \label{fig:head_groups_regional_density}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{tails_density.pdf}
        \caption{Tails}
        \label{fig:tails_regional_density}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{sodium_density.pdf}
        \caption{Sodium Ions}
        \label{fig:sodium_regional_density}
  \end{subfigure}
  \caption{In all cases, the component radial distribution functions are similar.
      They exhibit a composition gradient transitioning from the hydrophilic to the hydrophobic
          regions. The biggest differences are at r=0 where noise is higher due to
          decreased sampling. The center of the pore is not hollow, but contains sodium ions and
          head groups, even when the system is solvated. This architecture may impede transport in
          the real system in a chemically-dependent manner.
          The solvated system has a lower density of head groups near the
          pore center which is likely due to the swelling that is necessary in order to fit water
          molecules in the pore region.}~\label{fig:overlaid_densities}
  \end{figure}

@@

  \noindent We added additional water to our best Col\textsubscript{h} 
  phase model in order to create the H\textsubscript{II} phase.
  \begin{itemize}
    \item There have been a range of reported water contents used to 
    form the H\textsubscript{II} phase with this particular monomer.
    \item Although Resel et al. commented that the system is likely
    already fully hydrated at 7 wt \% water with additional water
    trapped in defects between mesophases.
    \item Therefore, we built two systems with 5 and 10 wt \% water.
  \end{itemize}

  \noindent We observed that water partitions into the distal tail region.
  \begin{itemize}
    \item We define the distal tail region to be any radial distance 
    greater than 1.5 nm from any pore center. 
    \item There is an approximately 3:2 ratio of water in the pores to
    water in the distal tails. 
    \item Due to the wedge shape of the monomers, the distal tail region
    has a relatively low density leaving space for water molecules to 
    fill.  
  \end{itemize}

  \noindent The pores of the H\textsubscript{II} phase are primarily a 
  mixture of water and sodium ions.
  \begin{itemize}
    \item The maximum density of head groups occurs 0.45 and 0.65 nm from
    the pore center in the 5 and 10 wt\% water systems respectively (see
    Figure~\ref{fig:component_densities}). 
    \item There are almost no head groups occupying the pore center.
  \end{itemize}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_dry.pdf}
  %BJC: simulation is extended to smooth out these curves
  \caption{Dry System}\label{fig:component_density_dry}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \vspace{-0.5cm}
  \includegraphics[width=\textwidth]{monomer_color_coded.pdf}
  \label{fig:monomer_color_coded}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_5wt.pdf}
  \caption{5 wt\% water}\label{fig:component_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_10wt.pdf}
  \caption{10 wt\% water}\label{fig:component_density_10wt}
  \end{subfigure}
  \caption{The radial densities of various monomer components paint a
  picture of the pore topology where the pore centers are primarily composed
  of water and sodium ions. The monomer groups labeled in each plot correspond to
  the color-coded monomer pictured in the upper right corner of the figure.
  All RDFs represent the number of atoms located at a given distance from the
  pore center normalized by the volume of the annular bin to which they belong.
  (a) In the dry system, the density of head groups and sodium ions are highest
  within 0.25 nm of the pore center. (b) In the 5 wt \% system, monomer head
  groups retreat about 0.2 nm radially in order to make room for water molecules.
  (c) Monomers in the 10 wt \% system retreat an additional 0.2 nm to make room
  for more water.}\label{fig:component_densities}
  \end{figure}

  \noindent Water and sodium transport is significantly faster in the less
  crowded 10 wt \% water pores. 
  \begin{itemize}
    \item The MSD of water is about 51 times higher and the MSD of sodium is
    about 49 times higher compared to 5 wt \% system.
    \item In general we observe similar solute transport mechanisms in the 5
    and 10 wt \% water systems but at different time scales.
    \item Therefore, we will focus on the 10 wt \% water system since we
    can collect a larger quantity of mechanistic data from the solute 
    trajectories.
  \end{itemize}

  \noindent We observed transport of 20 different small polar solutes in the
  pores of our model. 
  \begin{itemize}
    \item We created a separate initial configuration for each solute studied.
    \item We placed 6 solutes, equally spaced in $z$, in each nanopore.
    \item We allowed the solutes to simulate for 1 microsecond. 
  \end{itemize}

  \noindent The MSDs are not a monotonic function of solute size.
  \begin{itemize}
    \item In Figure~\ref{fig:all_msds_10wt}, we plotted the average
    MSD of each solute. 
    \item In Figure~\ref{fig:msd_radius_10wt}, we plotted solute
    MSDs against their molecular radius.
    \item We also plotted theoretical curves which illustrate the 
    expected MSD of each solute if they were to travel unhindered.
    \item We ensured that the Stokes-Einstein equation with the
    correction factor of Gierer and Wirtz passed through methanol 
    in order to give an approximate frame of reference. 
    \item Methanol is small and therefore can travel relatively
    unhindered compared to all other solutes.
    \item The theoretical line can be used as an approximate boundary
    between subdiffusive, Brownian and superdiffusive behavior.
  \end{itemize}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
  \caption{10 wt \% water}\label{fig:all_msds_10wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf}
  \caption{10 wt \% water}\label{fig:msd_radius_10wt}
  \end{subfigure}
  \caption{The MSDs of solutes in the 5 wt \% water system (a) are significantly
  smaller than those of the solutes in the 10 wt \% water system (b). The
  MSDs are not a monotonic function of molecular size (c and d). A significant
  number of solute MSDs fall below the theoretical lines predicted by the
  Stokes-Einstein equation and Gierer and Wirtz' corrected Stokes-Einstein equation.
  }\label{fig:msds}
  \end{figure}

% 5 and 10 wt %
%  \begin{figure}[!htb]
%  \centering
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
%  \caption{5 wt \% water}\label{fig:all_msds_5wt}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
%  \caption{10 wt \% water}\label{fig:all_msds_10wt}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{msd_radius_5wt.pdf}
%  \caption{5 wt \% water}\label{fig:msd_radius_5wt}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf}
%  \caption{10 wt \% water}\label{fig:msd_radius_10wt}
%  \end{subfigure}
%  \caption{The MSDs of solutes in the 5 wt \% water system (a) are significantly
%  smaller than those of the solutes in the 10 wt \% water system (b). The
%  MSDs are not a monotonic function of molecular size (c and d). A significant
%  number of solute MSDs fall below the theoretical lines predicted by the
%  Stokes-Einstein equation and Gierer and Wirtz' corrected Stokes-Einstein equation.
%  }\label{fig:msds}
%  \end{figure}

  \noindent Intermittent hops between long periods of entrapment lead
  to subdiffusive solute transport behavior. 
  \begin{itemize}
    \item As Figure~\ref{fig:msd_radius_10wt} implies, most solutes
    move significantly slower than expected.
    \item In Figure~\ref{fig:example_ztraces}, we've plotted the $z$-direction
    trajectory of three ethanol molecules.
    \item Typically, long periods of entrapment occur when ethanol 
    molecules are far from the pore center, while there is a much 
    greater degree of mobility close to the pore center.
    \item The MSD curve averaged over all ethanol trajectories is shown
    in Figure~\ref{fig:example_msd}.
    \item The curve is sub-linear and thus subdiffusive.
  \end{itemize}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{colorful_example_ztraces.pdf}
  \caption{}\label{fig:example_ztraces}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{example_msd.pdf}
  \caption{}\label{fig:example_msd}
  \end{subfigure}
  \caption{All solutes show subdiffusive transport behavior inside the membrane's
  nanopores, similar to that exhibited by ethanol. (a) The $z$-coordinate trace of
  3 representative ethanol COMs shows clear periods of entrapment separated by hops.
  In general, the longest dwell times occur when solutes are situated far from the
  pore center and the hops occur when solutes are close to the pore center. (b) The
  time-averaged MSD of ethanol is sub-linear which suggests transport is governed
  by an anomalous subdiffusion process.}\label{fig:qualitative_mechanisms}
  \end{figure}

  \noindent We observe three mechanisms of entrapment that are responsible for 
  subdiffusive behavior.
  \begin{enumerate}
    \item As already demonstrated in Figure~\ref{fig:example_ztraces}, solutes that
    drift away from the pore center can become entangled in the monomer tails. 
    \item Many of the solutes we studied are capable of donating hydrogen bonds to
    monomer head groups and thus are prone to temporary immobilization through this interaction.
    \item Because all solutes are polar, they have regions of concentrated electron
    density, modeled as partial charges, which can associate with sodium ions
    partially bound to monomer head groups.
  \end{enumerate}

  Due to the crowded environment among the monomer tails, solutes generally move faster
  in the less dense pore region.
  \begin{itemize}
    \item Figure~\ref{fig:hop_lengths} shows that this is the case for all solutes.
    \item Hops made in the pore region are on average 45 \% larger than those made
    outside the pore region.
  \end{itemize}

  However, time spent in the pore region does not necessarily result
  in a high MSD. 
  \begin{itemize}
    \item For example, ribose spends the largest fraction of time in 
    the pore center, but has the lowest hop frequency and the third 
    lowest average MSD (see Figures~\ref{fig:frac_time} and ~\ref{fig:hopfreq}).
  \end{itemize}

  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{hop_length.pdf}
  \caption{}\label{fig:hop_lengths}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{frac_time_spent.pdf}
  \caption{}\label{fig:frac_time}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{hopfreq_total.pdf}
  \caption{}\label{fig:hopfreq}
  \end{subfigure}
  \caption{(a) Hops made in the pore region of the 10 wt \% water system
  are, on average, 45 \% larger than those made outside the pore region.
  The trend in hop lengths is similar to the trend in MSDs shown in
  Figure~\ref{fig:all_msds_10wt} implying that solutes which make consistently
  larger hops have higher MSDs. The fraction of time spent by a solute in the
  pore region (b) does not necessarily lead to more frequent hopping (c). For
  example, ribose spends the largest fraction of time in the pore region, yet
  performs the the second lowest number of hops.}\label{fig:hops}
  \end{figure}

  \noindent The frequency with which solutes donate hydrogen bonds to monomer
  head groups is related to the number of hydrogen bond donating atoms as well
  as their identity.
  \begin{itemize}
    \item The percentage of solutes actively participating in at least one
    hydrogen bond with a head group each frame descends as the number of 
    hydroxyl groups decreases.
    \item Solutes that containing sulfur and nitrogen atoms in place of 
    oxygen atoms hydrogen bond less frequently since they are less 
    electronegative elements.
    \item The lifetime of hydrogen bonds follows nearly the same trend. Hydrogen
    bonds of solutes that hydrogen bond more frequently last longer. 
  \end{itemize}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{nhbonds_all.pdf}  % unique_hbonds.py
  \caption{}\label{fig:nhbonds}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{hbond_lifetime.pdf}  % hbond_dwells.py
  \caption{}\label{fig:hbond_dwells}
  \end{subfigure}
  \caption{(a) Solutes capable of donating hydrogen bonds to monomer head groups
  do so to varying degrees. The reported percentages represent unique solute-monomer
  hydrogen bonds. Individual solutes that hydrogen bond with multiple head groups
  simultaneously are only counted once. (b) The lifetime of individual hydrogen
  bonds appears correlated to the percentage of solutes involved in hydrogen bond
  interactions. Hydrogen bond lifetimes tend to be longer for solutes that
  hydrogen bond frequently. Note that solutes incapable of donating hydrogen
  bonds are omitted from this figure.}\label{fig:hbonds}
  \end{figure}

  \noindent Solutes with carbonyl groups tend to associate with sodium ions most frequently.
  \begin{itemize}
    \item The seven solutes that coordinate to sodium the most and 
    the six solutes with the longest association dwell times all contain 
    carbonyl groups, with the exception of DMSO which has an analagous sulfinyl group
    (see Figures~\ref{fig:all_solutes_NA_coordination} and~\ref{fig:all_NA_dwells}).
	\item Solutes with nitrogen atoms adjacent to the carbonyl groups tend to
	associate with sodium ions significantly more. 
  \end{itemize}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_solutes_NA_coordination.pdf}
  \caption{}\label{fig:all_solutes_NA_coordination}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_NA_dwells.pdf}
  \caption{}\label{fig:all_NA_dwells}
  \end{subfigure}
  \caption{(a) Solutes, especially those with carbonyl groups, spend a
  significant fraction of time coordinated to sodium ions. (b) The length
  of time a solute-sodium pairs spends associated tends to be higher for
  pairs that associate more frequently.}\label{fig:na_coordination}
  \end{figure}

@@

  \noindent The distribution of hop lengths is approximately Gaussian

@@

  Paralleling our work on the H\textsubscript{II} phase, our first task was to
  build a suitable unit cell representation of the Q\textsubscript{I} phase. 
  \begin{itemize}
    \item Unfortunately, the true space group of the Q\textsubscript{I}
    phase that we are studying is unknown. 
    \item Experimental diffraction has narrowed down the possible bicontinuous
    cubic configurations to the Ia3d and Pn3m space groups. 
    \item Therefore, we will build both types of unit cells and search for
    cues that can be used to differentiate them experimentally.
  \end{itemize}

  \noindent We have developed procedures to build both Ia3d and Pn3m unit
  cells.
  \begin{itemize}
    \item To our knowledge, nobody has ever built an atomistic bicontinuous
    cubic phase system without the aid of self-assembly.
    \item Self-assembly can be a long process, especially for fully atomistic
    systems. 
    \item Instead, we used known analytical equations that describe the 
    surface of these systems in order to place monomers into a unit cell.
    \item Monomers are placed perpendicular to the surface in random locations
    that don't overlap. One can control the pore size by translating monomers 
    perpendicular to the surface at the point where they are attached.
    %BJC: not sure how much more detail to include. Can go into a lot. Have to expand box and slowly compress. Add glycerol iteratively until there are no gaps.
  \end{itemize}
